Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
caption
conclusions 15

>>>>

\item SMBH feedback, unlike stellar heating sources, depends on the SMBH accretion rate, which is itself a function of the heating rate.  Compton heating is generally unimportant compared to stellar wind heating when the latter corresponds to the average SFH; however, Compton heating can dominate in the case of an impulsive burst of star formation (\ref{fig:vwSourcesImp}).  In principle the Compton heating rate is sufficiently high to prevent thermal instabilities in steady-state, i.e. $\dot{M}_{C} \lesssim \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth})  However, unlike local stellar feedback
mechanisms, SMBH feedback may not be capable of truly stabilizing the flow given its inability to respond instantaneously to local changes in the properties of the gas.  Kinetic feedback is more difficult to quantify, but could also be important in determining $\dot{M}(M_{\bullet}$) when stellar heating is weak ($\S\ref{sec:kinetic}$).
